%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}
    %------------------------------------------------
    \cventry
    {Eaton - eMobility Wireless} % Organization
    {Embedded Applications Engineer} % Job title
    {Port Coquitlam, BC} % Location
    {Jun. 2023 - Present} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item {Developed embedded applications for wireless controller and receiver products in embedded C, C++ and IEC 61131-3 structured text.}
            \item {Documented, investigated and fixed bugs in the firmware and embedded software of existing products.}
            \item {Authored and maintained configuration and testing software tools in VB, C\# and Python.}
            \begin{itemize}
                \item {Led the migration of one such tool from VB/WinForms to a cross platform GUI framework.}
            \end{itemize}
            \item {Planned software and hardware design activities in Jira.}
            \item {Helped develop next generation of wireless controller products from voice-of-customer and requirements gathering, through to detailed design execution.}
            \item {Utilized CANalyzer to develop and test CAN bus applications. }
        \end{cvitems}
    }

    %------------------------------------------------
    \cventry
    {Novarc Technologies, Inc.} % Organization
    {Director of Electrical R\&D} % Job title
    % {Principal Electrical Engineer - R\&D} % Job title
    {North Vancouver, BC} % Location
    {Jun. 2022 - Mar. 2023} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item {Created the proof of concept hardware and embedded software required to port our vision system and proprietary AI control to a 3rd party robotic
                        welding apparatus.}
            \begin{itemize}
                \item {Develop the firmware for low-level device drivers, including GPIO, UART, and I2C.}
                \item {Developed the software for the CAN 2.0A message handling, motion control functions, SPI accelerometer interface and a finite state machine in C++.}
                \item {The firmware/software was deployed to an Atmega32U4 based CAN development board to achieve the required motion control functions.}
            \end{itemize}
            \item {Established the PCB design capability within the R\&D and Engineering groups, including QA/QC and testing procedures.}
            % \item {Designed a 24V brushed DC motor driver PCB with tachometer circuitry to control a robotic wire feeder.}
            % \item {Guided the electrical and controls architecture and design requirements of the next generation products.}
        \end{cvitems}
    }

    %------------------------------------------------    

    \cventry
    {Novarc Technologies, Inc.} % Organization
    {Director of Electrical Engineering} % Job title
    % {Principal Electrical Engineer} % Job title
    {North Vancouver, BC} % Location
    {Mar. 2021 - Jun. 2022} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item {Responsible for EU Machinery and EMC Directive compliance of the Spool Welding Robot (SWR). Oversaw safety testing according to IEC 60204-1 and ISO/TS 15066, in addition to EMC testing according to IEC 61000-6-4.}
            \item {Head of the electrical engineering department with a team of two engineers under my direction.}
            \item {Planned and executed electrical and controls projects to implement new features on the SWR.}
        \end{cvitems}
    }

    %------------------------------------------------    
    \cventry
    {Ballard Power Systems} % Organization
    {Electrical Systems Engineer} % Job title
    {Burnaby, BC} % Location
    {Mar. 2020 - Mar. 2021} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item {Led the design of a CAN bus based hydrogen fuel cell voltage measurement device for use in a 1500VDC generation system. Developed schematics, BOM and PCB layout in Altium Designer.}
            \item {Designed and built a test apparatus to validate PCB re-work. Programmed test suite in IEC 61131-3 Structured Text for deployment to STW ESX controllers.}
            \item {Developed AC\&DC design specs, drawings, and calculations, for a 1.5MW stationary fuel cell generator intended for export to European markets.}
            \item {Investigated component failures on automotive fuel cell products to determine root cause and develop design solutions.}
        \end{cvitems}
    }

    %------------------------------------------------
    \cventry
    {Vard Electro Canada} % Organization
    {Electrical Engineer / Project Manager} % Job title
    {Vancouver, BC} % Location
    {Jul. 2017 - Mar. 2020} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item {Developed and executed the electrical scope (estimated at \$1.5M) of a project to retrofit a class of medium icebreakers for the Canadian Coast Guard.}
            \item {Managed a team of 7 engineers and designers on the fast- tracked detailed design phase of the project.}
            \item {Effectively communicated project scope, schedule, and budget with lead engineers.}
            \item {Reviewed weekly and monthly reports to track key performance metrics.}
        \end{cvitems}
    }

    %------------------------------------------------
    \cventry
    {Seaspan Vancouver Shipyards} % Organization
    {Electrical Systems Engineer(Contract)} % Job title
    {North Vancouver, BC} % Location
    {Jun. 2016 - Jul. 2017} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            % \item[]\textbf{Federal Fleet Renewal Program, Joint Support Ship}
            \item {Collaborated with an integrated project team to develop product requirements which met client performance specifications and complied with classification society (DNVGL) regulations.}
            \item {Responsible for performing reviews of electrical, electronic and communications systems design products to ensure technical accuracy and adherence to client and company standards.}
        \end{cvitems}
    }

    \cventry
    {Allnorth Consultants} % Organization
    {Electrical Engineer(Contract)} % Job title
    {Vancouver, BC} % Location
    {Jun. 2015 - Jun. 2016} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item {Performed AC load and short circuit studies as well as modelled LV and MV systems in EasyPower.}
            \item{Analyzed power factor of new and existing plant and provided recommendations for improvement.}
        \end{cvitems}
    }

    \cventry
    {Amec Foster Wheeler} % Organization
    {Electrical Engineer} % Job title
    {Vancouver, BC} % Location
    {Jun. 2012 - Jun. 2015} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item {Telecommunications system engineer tasked with system topography and detailed design including fibre optic communications system, telecommunications hardware, revenue metering and video surveillance system.}
        \end{cvitems}
    }
    \cventry
    {Autopro Automation} % Organization
    {Junior Engineer} % Job title
    {Burnaby, BC} % Location
    {May 2011 - Jun. 2012} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item {Assisted senior engineers with the design of control and automation systems for industrial plants.}
        \end{cvitems}
    }
\end{cventries}